Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-09-20 manuscript/manuscript.tex
Bit of editing in the linear density case

Lets perform a comparison between our numerical model and the
analytical solution for a spherical shell with a linear density
function like the following one:

\begin{equation}
    \rho(r') = ar' + b.
\end{equation}

Secondly we can analyse how the density-based discretization algorithm
works in case of a linear density function.
Because the absolute difference defined on equation
\ref{eq:density-abs-diff} will always be zero, the discretization
inequation \ref{eq:delta-density} will never be satisfied.
Therefore, independently of the linear function proposed, the
density-based algorithm will never be applied, leaving the modified
adaptive discretization algorithm as the only mechanism to control the
accuracy of the numerical approximation.
That's why, for linear density scenarios, we only need to determine
the minimum value of $D$ needed in order to guarantee an acceptable
accuracy while ignoring the value of $\delta$.

In order to compare the numerical model with the analytical solution we
must build a spherical shell made of tesseroids.
We propose a mesh of $30^\circ \times 30^\circ$ tesseroids whose outer and
inner radii are the same ones as the spherical shell in order to compute
the gravitational potential, the vertical component of the gradient
($g_z$) and the diagonal components of the Marussi tensor ($g_{xx}$,
$g_{yy}$, $g_{zz}$) on four different grids: (1) a grid located at the
pole, (2) another one on the Equator, (3) one located at satellite
height and (4) a big grid of $30^\circ \times 30^\circ$.
More information about this grids can be found on Table
\ref{tab:grids}.

>>>>

A spherical shell with a linear density function given by

\begin{equation}
    \rho(r') = ar' + b,
\end{equation}

\noindent
has an analytical solution given by Eq. \ref{eq:shell-pot-linear}.

The absolute density difference defined on equation
\ref{eq:density-abs-diff} will always be zero for the linear density case.
As a result, the inequality \ref{eq:delta-density} will always be satisfied and no
divisions will ever be performed.
Therefore, the distance-size ration $D$ of the adaptive discretization algorithm is the
only mechanism that controls the accuracy of the numerical integration.
For this reason, we will only determine the minimum value of $D$ needed in order to
guarantee an acceptable accuracy while ignoring the value of $\delta$.

In order to compare the numerical model with the analytical solution we
must build a spherical shell made of tesseroids.
We use a mesh of $30^\circ \times 30^\circ$ tesseroids whose outer and
inner radii are the same ones as the spherical shell in order to compute
the gravitational potential, the vertical component of the gradient
($g_z$), and the diagonal components of the Marussi tensor ($g_{xx}$,
$g_{yy}$, $g_{zz}$) on four different grids: (1) a grid located at the
pole, (2) another one on the Equator, (3) one located at satellite
height and (4) a big grid of $30^\circ \times 30^\circ$.
More information about this grids can be found on Table
\ref{tab:grids}.
